Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2024-01-06 Manuscript/Response to the Reviews.Rmd

8)  *"that was defective in NOS mutant (Figure 5I)" should be corrected as "Figure 5H".*

    We have corrected it.

9)  *Related to Figure 7, how do the larvae respond to a sequence of UV light (e.g. ten times 0.5s ON and 0.5 OFF) or ramping up/down UV light? Can the model make any predictions?*

    We performed new experiments, both in the mathematical model and in real calcium imaging, changing the amplitude and duration of UV stimulation. The results are shown in Figure 7A and B.

@@

We re-analysed previous single-cell data (Achim et al., 2018) and found no sGC homologues detected in cPRC and INNOS. However, a few were detected in INRGW. Additions were made to the supplement data regarding these data and the text was also amended.

*Page 10: "Diagram of the mathematical model with the components, interactions, parameters and equations used to model Ca dynamics." It would be helpful to include a legend explaining the meaning of each term (e.g. what is K, Co, Cp etc) and arrow color. Additionally, the main text should provide detailed descriptions to aid understanding.*

*Page 12: "This activated state is maintained for several tens of second." Can authors point out the data?*

In Figure4A and B, it can be seen that cPRC activity continues after UV stimulation.

@@

*Page 13: "In the Platynereis circuit, our mathematical model indicates that the magnitude of the NO-dependent signal depends on the intensity and duration of the UV/violet stimulus." Did the authors conduct experiments of various intensity and duration apart from modelling? If not, such experiments should be carried out to validate the mathematical model.*

We have performed a new calcium imaging experiment: a plot of the change in calcium levels in the cPRC when changing the power and duration of the UV stimulus is added in Figure7B.

### 2024-01-06 Manuscript/Manuscript.Rmd
Edited responses to reviewers
Update source data

---
title: Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit
author: 
  - name: "Kei Jokura<sup>1,`*`</sup>, Nobuo Ueda<sup>2</sup>, Martin Gühmann<sup>3</sup>, Luis Alfonso Yañez-Guerra<sup>1,4</sup>, Piotr Słowiński<sup>1</sup>, Kyle C. A. Wedgwood<sup>1</sup> and Gáspár Jékely<sup>1,5,`*`</sup>"
    affiliation: "<sup>1</sup>Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, United Kingdom <sup>2</sup>Okinawa Institute of Science and Technology, Okinawa, Japan, <sup>3</sup>School of Biological Sciences, University of Bristol, Bristol, United Kingdom, <sup>4</sup>School of Biological sciences, University of Southampton, Southampton, United Kingdom, <sup>5</sup>Centre for Organismal Studies (COS), University of Heidelberg, 69120 Heidelberg, Germany  <br> <sup>*</sup>Correspondence`:` k.jokura @ exeter.ac.uk, gaspar.jekely @ cos.uni-heidelberg.de"
output:
  html_document:
    theme: lumen
  word_document: default
  pdf_document:
    latex_engine: lualatex
    template: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r echo=FALSE,fig.cap="**Figure 3. NOS is required for UV avoidance in *Platynereis* larvae.**  (**A**) Swimming trajectories of wild type (WT, n=32) and *NOS* mutant (*NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) three-day-old larvae. All trajectories start at 0 x and y position and time 0 corresponding to 10 sec before the onset of 395 nm stimulation from the side. (**B**) Vertical position of batches of wild type and mutant three-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. (**C**) Comparison of vertical position of wild type and mutant three-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. The wild type (WT, n=32) and *NOS* mutant (*NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) larvae. (**D**) Vertical displacement in 30 sec bins of wild type (10 batches) and mutant (*NOSΔ11/Δ11*, 5 batches and *NOSΔ23/Δ23*, 7 batches) three-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. (**E**) Vertical position of batches of control and L-NAME-treated (0.1 and 1 mM) three-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. (**F**) Comparison of vertical position of control (n=6) and L-NAME-treated (0.1 and 1 mM, n=6 each) three-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. (**G**) Vertical displacement in 30 sec bins of control (15 batches) and L-NAME-treated (0.1 and 1 mM, 15 batches each) three-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. <br> Figure 3 -- source data 1-5. Source data for panels A-E."}

@@

```{r echo=FALSE,fig.cap="**Figure 4. NOS and two NIT-GCs shape Ca^2+^ signals during cPRC UV/violet response.** (**A**, **B**) GCaMP6s signals in cPRCs in wild type and *NOS* mutant (A, *NOSΔ11/Δ11*, B, *NOSΔ23/Δ23*) larvae during 405 nm light stimulation. (**C**, **D**) In situ HCR for (C) *NIT-GC1* and (D) *NIT-GC2* (magenta) in three-day-old *Platynereis* larvae. Larvae were co-stained with an antibody against acetylated α-tubulin to label cPRC cilia and the neuropil (green). (**E**, **F**) Immunostaining for (E) NIT-GC1 and (F) NIT-GC2 (magenta), co-stained for acetylated α-tubulin (green). (**G**) The domain structure of *Platynereis* NIT-GC1 and the truncated NIT-GC1ΔNIT protein lacking the NIT domain. A predicted transmembrane region (TM) is shown in grey. (**H**) Schematic of the cell-based assay to detect cGMP production following the addition of an NO donor SNAP or DMSO as control. (**I**-**L**) Green cGull fluorescence over time for the four conditions tested. Individual responses and their mean with 0.95 confidence interval are shown (n > 6 cells). Intensities are normalized (ΔF/F0). The indicated chemicals were added at 2 min after the start of imaging (grey bars). (**M**, **N**) GCaMP6s signals in cPRCs in (M) NIT-GC1 and (N) NIT-GC2 morphant larvae during 405 nm light stimulation. Individual responses and their mean with 0.95 confidence interval are shown. <br> Figure 4 -- source data 1-8. Source data for panels A, B and I-N."}

knitr::include_graphics(path = "figures/Fig4.png")

@@

```{r echo=FALSE,fig.cap="**Figure 7. Comparison of the magnitude of cPRC activation as a function of stimulus duration and intensity.** (**A**) Change in magnitude calculated from mathematical models. Median values of the $AUP$ are presented as a heatmap with dark blue indicating flat $C_P(t)$ traces with median $AUP$ close to 0 and red indicating that the $C_P(t)$ traces have a clearly defined delayed activation peak. (**B**) Change in magnitude calculated from experiments data. The amount of change in cPRC fluorescence intensity (ΔF/F0) when the laser power (%) and time duration (seconds) of the stimulus are varied using calcium imaging. Laser power is shown as relative values. "}

@@

```{r echo=FALSE,fig.cap="**Figure 3 -- figure supplement 2. Generation and behavioural characterisation of *NOS* CRISPR knockouts.** (**A**) Schematic diagram of the set-up of the behavioural experiment. (**B**) Swimming trajectories of wild type (WT, n=37) and *NOS* mutant (NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) two-day-old larvae. All trajectories start at 0 x and y position and time 0 corresponding to 10 sec before the onset of 395 nm stimulation from the side. (**C**)  Vertical displacement in 30 sec bins of wild type (WT, n=37) and mutant (NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) two-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. (**D**) Comparison of vertical position of wild type and mutant two-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. The wild type (WT, n=52) and *NOS* mutant (*NOSΔ11/Δ11*, n=30 and *NOSΔ23/Δ23*, n=16) larvae. (**E**) Vertical position of batches of wild type (12 batches) and mutant (NOSΔ11/Δ11, 8 batches and NOSΔ23/Δ23, 3 batches) two-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. <br> Figure 3 -- figure suppmenet 1 -- source data 1-6. Source data for panels B-G."}
knitr::include_graphics(path = "figures/Fig3_sup2.png")

@@

```{r echo=FALSE,fig.cap="**Figure 3 -- figure supplement 3. Generation and behavioural characterisation of *NOS* CRISPR knockouts.** (**A,B**) Swimming speed of batches of wild type and *NOS* mutant two-day-old (WT, n=37, NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) (A) and three-day-old (WT, n=32, *NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) (B) larvae under 395 nm UV stimulation. (**C,D**) Mean swimming speed of wild type and *NOS* mutant two-day-old (WT, n=37, NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) (C) and three-day-old (WT, n=32, *NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) (D) larvae during 10 seconds before (dark) and 10 seconds after the start of 395 nm UV stimulation (sideUV). Data points for the same larva are joined by lines. One-tailed paired t-test; p-values (‘***’ <0.001) are shown. (**E,F**) Average ciliary beat frequency of wild type and mutant two-day-old (E) and three-day-old (F) single larvae during 10 seconds before (gray) and 10 seconds after the start of 395 nm UV stimulation (purple). N=6 larvae each. Data points for the same larva are joined by lines. One-tailed paired t-test; p-values (‘**’ <0.01 or ‘*’ <0.05) are shown. <br> Figure 3 -- figure suppmenet 2 -- source data 1-6. Source data for panels B-G."}
knitr::include_graphics(path = "figures/Fig3_sup3.png")

@@

```{r echo=FALSE,fig.cap="**Figure 4 -- figure supplement 3. Expression of NIT-GC1 and NIT-GC2 in the cPRCs** (**A**) HCR co-expression analysis of *NIT-GC1* (magenta) and *MLD/pedal-peptide-2 proneuropeptide* (green). Anterior view of a two-day-old larva. Nuclei were stained with DAPI (cyan). **(B, C)** Expression of *NIT-GC2* (magenta) detected by in situ HCR. Anterior (B) and ventral (C) views of a three-day-old larva. Nuclei were stained with DAPI (cyan). **(D, E)** Immunostaining for NIT-GC1 (D) and NIT-GC2 (E) antibodies in larvae injected with NIT-GC1 (D) or NIT-GC2 (E) morpholinos. Acetylated α-tubulin staining (green) highlights the neuropil and cPRC cilia. Anterior view of a two-day-old larva. (**F**) The fluorescence intensities of the NIT-GC1 or NIT-GC2 in the control and morphant (MO1 and MO2) larvae (n=6 each) were normalized to the Acetylated α-tubulin signals and plotted as a relative fluorescence. One-way ANOVA with Dunnett’s multiple-comparison test; p-values (‘***’ <0.001) are shown."}
knitr::include_graphics(path = "figures/Fig4_sup3.png")

@@

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 1. Simulated Ca^2+^ traces for parameter sets fitted to individual Ca^2+^-recordings collected in wild type, *NOS* knockout, and *NIT-GC2* morphant larvae.** (**A-C**) Simulated Ca^2+^ traces in cPRC (A), INNOS (B) and INRGW (C) cells in the wild-type condition. (**D-F**) Simulated Ca^2+^ traces in cPRC (D), INNOS (E) and INRGW (F) cells in the *NOS*-knockout condition. (**G-I**) Simulated Ca^2+^ traces in cPRC (G), INNOS (H) and INRGW (I) cells in the *NIT-GC2*-morphant condition. Thin coloured curves indicate individual recordings (cPRC - purple, INNOS - blue and INRGW - green), thin grey curves indicate simulated Ca^2+^ traces based on model parameters fitted to the individual recording, thick coloured curves indicate averages of the recordings and thick black curves represent the average of the fits. "}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl1.svg")

@@

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 2. Comparison of fits with different fixed parameter sets when fitting the WT model to individual recordings from the WT INRGW cells.** Panels A-B, D-E, G-H  (column fixed parameters) show simulated traces of the Ca^2+^ levels in cPRC and INNOS cells produced by different fixed parameter sets. Panels C, F and I show individual recordings fitted to the data from INRGW cells."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl2.svg")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 3. Comparison of fits to the cPRC recordings from NIT-GC2 morphant larvae using the NIT-GC2 morpholino model or the NOS-knockout model.**  Thin coloured curves indicate individual recordings, thin grey curves are simulated Ca^2+^ traces, thick coloured curves indicate averages of the recordings and thick black curves represent the mean of the fits."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl3.svg")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 4. Distributions of the parameter values fitted to the cPRC recordings.** Violin plots (grey lines) are kernel density estimates of the underlying distributions; computed using the Matlab function *ksdensity* with default settings, i.e., using normal kernel function, plots are trimmed to the observed range of data. Markers represent individual parameter values, white markers indicate medians, vertical grey bars indicate interquartile range (Q25 to Q75), and the dashed line indicates the value 1. Where violin plots are not shown, these parameters are associated with terms/equations that are excluded from the fitting procedure (see Methods for details)." }
knitr::include_graphics(path = "figures/Figure6_fig_Suppl4.svg")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 5. Pairwise correlations between parameters of the WT model fitted to WT cPRC recordings** Parameters associated with the $C_R$ equation are not included (see Methods for details). Panels on the diagonal show kernel density estimates of the distributions of the individual parameters; computed using Matlab function *ksdensity* with default settings, i.e., using normal kernel function, plots are trimmed to the observed range of data. The other panels show kernel density estimates of bivariate distributions of pairs of parameters (heatmaps; darker colours indicate higher density). Also shown using markers are the values of the individual parameter combinations."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl5.svg")
```

>>>>

---
title: Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit
author: 
  - name: "Kei Jokura<sup>1,`*`</sup>, Nobuo Ueda<sup>2</sup>, Martin Gühmann<sup>3</sup>, Luis Alfonso Yañez-Guerra<sup>1,4</sup>, Piotr Słowiński<sup>1</sup>, Kyle C. A. Wedgwood<sup>1</sup> and Gáspár Jékely<sup>1,5,`*`</sup>"
    affiliation: "<sup>1</sup>Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, United Kingdom <sup>2</sup>Okinawa Institute of Science and Technology, Okinawa, Japan, <sup>3</sup>School of Biological Sciences, University of Bristol, Bristol, United Kingdom, <sup>4</sup>School of Biological sciences, University of Southampton, Southampton, United Kingdom, <sup>5</sup>Centre for Organismal Studies (COS), University of Heidelberg, 69120 Heidelberg, Germany  <br> <sup>*</sup>Correspondence`:` k.jokura @ exeter.ac.uk, gaspar.jekely @ cos.uni-heidelberg.de"
output:
  pdf_document:
    latex_engine: lualatex
    template: default
  html_document:
    theme: lumen
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r echo=FALSE,fig.cap="**Figure 3. NOS is required for UV avoidance in *Platynereis* larvae.**  (**A**) Swimming trajectories of wild type (WT, n=32) and *NOS* mutant (*NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) three-day-old larvae. All trajectories start at 0 x and y position and time 0 corresponding to 10 sec before the onset of 395 nm stimulation from the side. (**B**) Vertical position of batches of wild type and mutant three-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. (**C**) Comparison of vertical position of wild type and mutant three-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. The wild type (WT, n=32) and *NOS* mutant (*NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) larvae. (**D**) Vertical displacement in 30 sec bins of wild type (10 batches) and mutant (*NOSΔ11/Δ11*, 5 batches and *NOSΔ23/Δ23*, 7 batches) three-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. (**E**) Vertical position of batches of control and L-NAME-treated (0.1 and 1 mM) three-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. (**F**) Comparison of vertical position of control (n=6) and L-NAME-treated (0.1 and 1 mM, n=6 each) three-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. (**G**) Vertical displacement in 30 sec bins of control (15 batches) and L-NAME-treated (0.1 and 1 mM, 15 batches each) three-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. <br> Figure 3 -- source data 1-7. Source data for panels A-G."}

@@

```{r echo=FALSE,fig.cap="**Figure 4. NOS and two NIT-GCs shape Ca^2+^ signals during cPRC UV/violet response.** (**A**, **B**) GCaMP6s signals in cPRCs in wild type and *NOS* mutant (A, *NOSΔ11/Δ11*, B, *NOSΔ23/Δ23*) larvae during 405 nm light stimulation. (**C**, **D**) In situ HCR for (C) *NIT-GC1* and (D) *NIT-GC2* (magenta) in three-day-old *Platynereis* larvae. Larvae were co-stained with an antibody against acetylated α-tubulin to label cPRC cilia and the neuropil (green). (**E**, **F**) Immunostaining for (E) NIT-GC1 and (F) NIT-GC2 (magenta), co-stained for acetylated α-tubulin (green). (**G**) The domain structure of *Platynereis* NIT-GC1 and the truncated NIT-GC1ΔNIT protein lacking the NIT domain. A predicted transmembrane region (TM) is shown in grey. (**H**) Schematic of the cell-based assay to detect cGMP production following the addition of an NO donor SNAP or DMSO as control. (**I**-**L**) Green cGull fluorescence over time for the four conditions tested. Individual responses and their mean with 0.95 confidence interval are shown (n > 6 cells). Intensities are normalized (ΔF/F0). The indicated chemicals were added at 2 min after the start of imaging (grey bars). (**M**, **N**) GCaMP6s signals in cPRCs in (M) NIT-GC1 and (N) NIT-GC2 morphant larvae during 405 nm light stimulation. Individual responses and their mean with 0.95 confidence interval are shown. <br> Figure 4 -- source data 1-8. Source data for panels A, B and I-N."}
knitr::include_graphics(path = "figures/Fig4.png")

@@

```{r echo=FALSE,fig.cap="**Figure 7. Comparison of the magnitude of cPRC activation as a function of stimulus duration and intensity.** (**A**) Change in magnitude calculated from mathematical models. Median values of the $AUP$ are presented as a heatmap with dark blue indicating flat $C_P(t)$ traces with median $AUP$ close to 0 and red indicating that the $C_P(t)$ traces have a clearly defined delayed activation peak. (**B**) Change in magnitude calculated from experiments data. The amount of change in cPRC fluorescence intensity (ΔF/F0) when the laser power (%) and time duration (seconds) of the stimulus are varied using calcium imaging. The intensity change is indicated by the size of the circle and the colour gradient from blue to red. Laser power is shown as relative values. <br> Figure 7 -- source data 1. Bubble chart readings. "}

@@

```{r echo=FALSE,fig.cap="**Figure 3 -- figure supplement 2. Generation and behavioural characterisation of *NOS* CRISPR knockouts.** (**A**) Schematic diagram of the set-up of the behavioural experiment. (**B**) Swimming trajectories of wild type (WT, n=37) and *NOS* mutant (NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) two-day-old larvae. All trajectories start at 0 x and y position and time 0 corresponding to 10 sec before the onset of 395 nm stimulation from the side. (**C**)  Vertical displacement in 30 sec bins of wild type (WT, n=37) and mutant (NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) two-day-old larvae stimulated with 395 nm light from the side, 488 nm light from the top and 395 nm light from the top. (**D**) Comparison of vertical position of wild type and mutant two-day-old larvae after 30 seconds of UV stimulation. One-way ANOVA with Dunnett’s multiple-comparison test are shown. The wild type (WT, n=52) and *NOS* mutant (*NOSΔ11/Δ11*, n=30 and *NOSΔ23/Δ23*, n=16) larvae. (**E**) Vertical position of batches of wild type (12 batches) and mutant (NOSΔ11/Δ11, 8 batches and NOSΔ23/Δ23, 3 batches) two-day-old larvae over time under 395 nm UV stimulation. The starting position of each larval trajectory was set to 0. One-way ANOVA with Dunnett’s multiple-comparison test are shown. *P < 0.05. <br> Figure 3 -- figure suppmenet 2 -- source data 1-4. Source data for panels B-E."}
knitr::include_graphics(path = "figures/Fig3_sup2.png")

@@

```{r echo=FALSE,fig.cap="**Figure 3 -- figure supplement 3. Generation and behavioural characterisation of *NOS* CRISPR knockouts.** (**A,B**) Swimming speed of batches of wild type and *NOS* mutant two-day-old (WT, n=37, NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) (A) and three-day-old (WT, n=32, *NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) (B) larvae under 395 nm UV stimulation. (**C,D**) Mean swimming speed of wild type and *NOS* mutant two-day-old (WT, n=37, NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) (C) and three-day-old (WT, n=32, *NOSΔ11/Δ11*, n=26 and *NOSΔ23/Δ23*, n=47) (D) larvae during 10 seconds before (dark) and 10 seconds after the start of 395 nm UV stimulation (sideUV). Data points for the same larva are joined by lines. One-tailed paired t-test; p-values (‘***’ <0.001) are shown. (**E,F**) Average ciliary beat frequency of wild type and mutant two-day-old (E) and three-day-old (F) single larvae during 10 seconds before (gray) and 10 seconds after the start of 395 nm UV stimulation (purple). N=6 larvae each. Data points for the same larva are joined by lines. One-tailed paired t-test; p-values (‘**’ <0.01 or ‘*’ <0.05) are shown. <br> Figure 3 -- figure suppmenet 3 -- source data 1-6. Source data for panels A-F."}
knitr::include_graphics(path = "figures/Fig3_sup3.png")

@@

```{r echo=FALSE,fig.cap="**Figure 4 -- figure supplement 3. Expression of NIT-GC1 and NIT-GC2 in the cPRCs** (**A**) HCR co-expression analysis of *NIT-GC1* (magenta) and *MLD/pedal-peptide-2 proneuropeptide* (green). Anterior view of a two-day-old larva. Nuclei were stained with DAPI (cyan). **(B, C)** Expression of *NIT-GC2* (magenta) detected by in situ HCR. Anterior (B) and ventral (C) views of a three-day-old larva. Nuclei were stained with DAPI (cyan). **(D, E)** Immunostaining for NIT-GC1 (D) and NIT-GC2 (E) antibodies in larvae injected with NIT-GC1 (D) or NIT-GC2 (E) morpholinos. Acetylated α-tubulin staining (green) highlights the neuropil and cPRC cilia. Anterior view of a two-day-old larva. (**F**) The fluorescence intensities of the NIT-GC1 or NIT-GC2 in the control and morphant (MO1 and MO2) larvae (n=6 each) were normalized to the Acetylated α-tubulin signals and plotted as a relative fluorescence. One-way ANOVA with Dunnett’s multiple-comparison test; p-values (‘***’ <0.001) are shown. <br> Figure 4 -- figure suppmenet 3 -- source data 1. Comparison NIT-GCs signals readings."}
knitr::include_graphics(path = "figures/Fig4_sup3.png")

@@

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 1. Simulated Ca^2+^ traces for parameter sets fitted to individual Ca^2+^-recordings collected in wild type, *NOS* knockout, and *NIT-GC2* morphant larvae.** (**A-C**) Simulated Ca^2+^ traces in cPRC (A), INNOS (B) and INRGW (C) cells in the wild-type condition. (**D-F**) Simulated Ca^2+^ traces in cPRC (D), INNOS (E) and INRGW (F) cells in the *NOS*-knockout condition. (**G-I**) Simulated Ca^2+^ traces in cPRC (G), INNOS (H) and INRGW (I) cells in the *NIT-GC2*-morphant condition. Thin coloured curves indicate individual recordings (cPRC - purple, INNOS - blue and INRGW - green), thin grey curves indicate simulated Ca^2+^ traces based on model parameters fitted to the individual recording, thick coloured curves indicate averages of the recordings and thick black curves represent the average of the fits. "}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl1.png")

@@

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 2. Comparison of fits with different fixed parameter sets when fitting the WT model to individual recordings from the WT INRGW cells.** Panels A-B, D-E, G-H  (column fixed parameters) show simulated traces of the Ca^2+^ levels in cPRC and INNOS cells produced by different fixed parameter sets. Panels C, F and I show individual recordings fitted to the data from INRGW cells."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl2.png")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 3. Comparison of fits to the cPRC recordings from NIT-GC2 morphant larvae using the NIT-GC2 morpholino model or the NOS-knockout model.**  Thin coloured curves indicate individual recordings, thin grey curves are simulated Ca^2+^ traces, thick coloured curves indicate averages of the recordings and thick black curves represent the mean of the fits."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl3.png")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 4. Distributions of the parameter values fitted to the cPRC recordings.** Violin plots (grey lines) are kernel density estimates of the underlying distributions; computed using the Matlab function *ksdensity* with default settings, i.e., using normal kernel function, plots are trimmed to the observed range of data. Markers represent individual parameter values, white markers indicate medians, vertical grey bars indicate interquartile range (Q25 to Q75), and the dashed line indicates the value 1. Where violin plots are not shown, these parameters are associated with terms/equations that are excluded from the fitting procedure (see Methods for details)." }
knitr::include_graphics(path = "figures/Figure6_fig_Suppl4.png")
```

```{r echo=FALSE,fig.cap="**Figure 6 -- figure supplement 5. Pairwise correlations between parameters of the WT model fitted to WT cPRC recordings** Parameters associated with the $C_R$ equation are not included (see Methods for details). Panels on the diagonal show kernel density estimates of the distributions of the individual parameters; computed using Matlab function *ksdensity* with default settings, i.e., using normal kernel function, plots are trimmed to the observed range of data. The other panels show kernel density estimates of bivariate distributions of pairs of parameters (heatmaps; darker colours indicate higher density). Also shown using markers are the values of the individual parameter combinations."}
knitr::include_graphics(path = "figures/Figure6_fig_Suppl5.png")
```
